---
title: "Assignment 7"
author: "Surplus Value"
date: "3/8/2018"
output: slidy_presentation
---


```{r, echo=FALSE, cache=FALSE, results='asis', warning=FALSE, comment=FALSE, warning=FALSE}
library(magrittr)
library(dplyr)
library(MASS)
library(purrr)
library(pwr)
library(PASWR)
library(Hmisc)
library(AER)
library(knitr)
```
  



```{r, echo=FALSE}

RSdata <- read.csv("~/Desktop/Ph.D./Econometrics/240A/R Problem Sets /Homework 7/RSdata.csv")

RSdata <- transform(RSdata,
                    ln_area = log(area),
                    ln_yield = log(prod))
```



##### Number 1: Naive Elasticities using OLS
```{r echo=FALSE, results='asis'}

Reg_Supply <- lm(ln_qs ~ ln_fp + trendsp1+ trendsp2 +trendsp3 , RSdata)
Reg_Demand <- lm(ln_qd ~ ln_sp + trendsp1 + trendsp2 +trendsp3 , RSdata)

OLS_Supply <- as.data.frame(Reg_Supply$coefficients)
OLS_Demand <- as.data.frame(Reg_Demand$coefficients)

kable(OLS_Supply)
kable(OLS_Demand)

```

##### Number 2: Estimation with IV

```{r echo=FALSE, results='asis'}

RegIV_Supply <- ivreg(ln_qs ~ ln_fp + ln_w + trendsp1+ trendsp2 +trendsp3 | ln_w + lag_ln_w + trendsp1 + trendsp2 +trendsp3, data=RSdata)
RegIV_Demand <- ivreg(ln_qd ~ ln_sp + trendsp1+ trendsp2 +trendsp3 | ln_w + trendsp1 + trendsp2 +trendsp3, data=RSdata)

IV_Supply <- as.data.frame(RegIV_Supply$coefficients)
IV_Demand <- as.data.frame(RegIV_Demand$coefficients)

kable(IV_Supply)
kable(IV_Demand)
```

##### Number 3: Haussman Test

```{r echo=FALSE, results='asis'}

betaOLS_Supply <- coeftest(Reg_Supply)[2,1]
betaOLS_Supply_Var <- (coeftest(Reg_Supply)[2,2])^2

betaOLS_Demand <- coeftest(Reg_Demand)[2,1]
betaOLS_Demand_Var <- (coeftest(Reg_Demand)[2,2])^2

betaIV_Supply <- coeftest(RegIV_Supply)[2,1]
betaIV_Supply_Var <- (coeftest(RegIV_Supply)[2,2])^2

betaIV_Demand <- coeftest(RegIV_Demand)[2,1]
betaIV_Demand_Var <- (coeftest(RegIV_Demand)[2,2])^2


Haus_Supply <- (betaOLS_Supply-betaIV_Supply)^2/(betaIV_Supply_Var - betaOLS_Supply_Var) 
Haus_Demand <- (betaOLS_Demand-betaIV_Demand)^2/(betaIV_Demand_Var - betaOLS_Demand_Var) 

Haussman_Supply <- as.data.frame(Haus_Supply)
Haussman_Demand <- as.data.frame(Haus_Demand)

kable(Haussman_Supply)
kable(Haussman_Demand)

```

#####Number 4: Using Area as the Dependent Variable

The supply elasticity for area is smaller than the supply elasticity for quantity by approximately 0.023.



```{r echo=FALSE, results='asis'}



RegIV_Supply_area <- ivreg(ln_area ~ ln_fp + ln_w + trendsp1+ trendsp2 +trendsp3 | ln_w + lag_ln_w + trendsp1 + trendsp2 +trendsp3, data=RSdata)



IV_AY <- as.data.frame(RegIV_Supply_area$coefficients)

kable(IV_AY)
```

#####Number 5

We found some slight differences between our coefficient estimates and the ones reported in Roberts and Schlenker (2013) which had seven years less of data.

```{r, echo=FALSE}

```

#####Number 6

In general, the file containing the data is well structured. It contains a "Read me" file that navigates the reader through the steps the authors did. As a minor recommendation, they could have used GitHub. 

```{r, echo=FALSE}

```

